### 2019-01-10 Sections/costs_and_attributes_in_quantum_networks.tex
Minor edits

Because spectral filtering can be regarded as a frequency-dependent loss channel, its associated cost can be treated in the same manner, except that rather than keeping track of a single efficiency $\eta$, we track a frequency response function $\eta_f(\omega)$, with the same multiplicative property,
\begin{align}
	\eta_f^\mathrm{(net)}(\omega)=\prod_i \eta_f^{(i)}(\omega).
\end{align}

@@

For two classical distributions, the classical mutual information is given by,
\begin{align}\index{Mutual information}
I(A;B) = H(A) + H(B) - H(A,B).
\end{align}
Analogously, the quantum mutual information  for bipartite state $\hat\rho_{A,B}$ is defined as,
\begin{align}
I(A;B)_{\hat\rho} = S(\hat\rho_A) + S(\hat\rho_B) - S(\hat\rho_{A,B}),
\end{align}
using the von Neuman entropy.

@@

And the \textit{classical channel capacity} of $\mathcal{E}$ is defined as
\begin{align}\index{Classical!Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{1}{n} I(\mathcal{E}^{\otimes n}),
\end{align}
\comment{Added missing entropy/capacity measure in here that needs to act on E. Correct?}
which can be interpreted as the maximum bitrate of the channel, per use of the channel, in the limit of an infinite number of uses.
(Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).\comment{Why is this called the same thing as before but defined differently and using a different symbol for the metric?}

@@

The \textit{quantum channel capacity}\index{Quantum channel capacity} is then analogously defined as,
\begin{align}\label{eq:quantcohinfo}
Q(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{1}{n} \mathcal{I}_Q(\mathcal{E}^{\otimes n}).
\end{align}

@@

\comment{This is an excellent idea to have a table summarising the different channel capacity measures!! Good thinking! Perhaps also have a column describing the interpretation of the measure, in English rather than in maths.}
% A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacitie}.
% \begin{widetext}
% \begin{table}[hbt]
% \begin{tabular}{ |c | c | c| c| } \hline
% Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
% Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
% % Entanglement Assisted Classical & Classical information & Quantum mutual information &Bennett-Shor-Smolin-Thapliyal formula \\
% Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
% \end{tabular}
% \caption{\label{tab:capacitie} Measure of classical and quantum channel capacities.}
% \end{table}
% \end{widetext}

>>>>

Because spectral filtering can be regarded as a frequency-dependent loss channel, its associated cost can be treated in the same manner, except that rather than keeping track of a single efficiency $\eta$, we track a frequency response function $\eta_f(\omega)$, with the same multiplicative property (on a per-frequency basis),
\begin{align}
	\eta_f^\mathrm{(net)}(\omega)=\prod_i \eta_f^{(i)}(\omega).
\end{align}

@@

For two classical distributions, the classical mutual information is given by,
\begin{align}\index{Mutual information}
I(A;B) = H(A) + H(B) - H(A,B).
\end{align}
Analogously, the quantum mutual information\index{Quantum mutual information} for bipartite state $\hat\rho_{A,B}$ is defined as,
\begin{align}
I(A;B)_{\hat\rho} = S(\hat\rho_A) + S(\hat\rho_B) - S(\hat\rho_{A,B}),
\end{align}
using the von Neuman entropy.

@@

And the \textit{classical channel capacity} of $\mathcal{E}$ is defined as
\begin{align}\index{Classical!Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{I(\mathcal{E}^{\otimes n})}{n},
\end{align}
\comment{Added missing entropy/capacity measure in here that needs to act on E. Correct?}
which can be interpreted as the maximum bitrate of the channel, per use of the channel, in the limit of an infinite number of uses, where entangled between multiple applications is allowed in general.\comment{Why is this called the same thing as before but defined differently and using a different symbol for the metric?}

@@

The \textit{quantum channel capacity}\index{Quantum channel capacity} is then analogously defined as,
\begin{align}\label{eq:quantcohinfo}
Q(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{\mathcal{I}_Q(\mathcal{E}^{\otimes n})}{n}.
\end{align}

@@

\comment{This is an excellent idea to have a table summarising the different channel capacity measures!! Good thinking! Perhaps also have a column describing the interpretation of the measure, in English rather than in maths.}
% A summary of the different measure of classical and quantum capacities are given in Table \ref{tab:capacities}.
% \begin{widetext}
% \begin{table}[hbt]
% \begin{tabular}{ |c | c | c| c| } \hline
% Capacity & Type of information & Correlation measure &Capacity formula  \\ \hline
% Classical &Classical information &Holevo information &Eq.~(\ref{eq:holevoinfo})       \\
% % Entanglement Assisted Classical & Classical information & Quantum mutual information &Bennett-Shor-Smolin-Thapliyal formula \\
% Quantum &Quantum information &Quantum Coherent Information &Eq.~(\ref{eq:quantcohinfo}) \\ \hline
% \end{tabular}
% \caption{\label{tab:capacities} Measure of classical and quantum channel capacities.}
% \end{table}
% \end{widetext}
